%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Associate profressor} % Job title
{\href{https://www.bordeaux-inp.fr/en}{Bordeaux INP}} % Organisation
{Talence - France} % Location
{Since Sept. 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Teaching: ENSEIRB-Matmeca, mostly in analog electronics}
    \item {Research: IMS lab, BioElectronique group - TIPS. \underline{keywords:} bioelectronics, instrumentation for bio-sciences,multiphysics and modeling of bio-electronic interfaces}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Associate profressor} % Job title
    {\href{www.cyu.fr}{CY Cergy Paris Université}} % Organisation
    {Cergy - France} % Location
    {Sept. 2016 - Sept. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching: IUT - GEII department (Electrical Engineering) ; mostly in electronics, control theory and mathematics}
        \item {Research: ETIS lab, CELL group}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {French CNRS sabatical year} % Job title
    {\href{https://www.lirmm.fr}{LIRMM lab}} % Organisation
    {Montpellier - France} % Location
    {Sept. 2020 - Sept. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Micro-électronique department}
        \item {SmartIES group}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Officer - Brain Computer Interfaces and Neural Engineering Lab} % Job title
    {\href{https://www.essex.ac.uk/departments/computer-science-and-electronic-engineering/research/brain-computer-interfaces-and-neural-engineering}{University of Essex}} % Organisation
    {Colchester - United Kingdom} % Location
    {Sept. 2015 - Sept. 2016} % Date(s)
    {
      Multiphics modeling of micro-electrode implantation and electrical stimulation of peripheral nerve for sensorimotor rehabilitation.
    }

%---------------------------------------------------------
  \cventry
    {PhD student then Assistant Professor} % Job title
    {\href{https://www.u-bordeaux.fr}{University of Bordeaux}} % Organisation
    {Talence - France} % Location
    {Sept. 2011 - Sept. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching: 2011-2012 ENSEIRB-Matmeca , 2012-2015 IUT GEII (Electrical Engineering department) University of Bordeaux}
        \item {Research: Design and modeling of circuits and systems for neural stimulation in different pathologic an experimental contexts.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
