%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------


\cvsection{Scientific Publications}

\cvsubsection{Journals}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}
%---------------------------------------------------------
  \cvskill
    {[J01]} % Interest
    {Regnacq, L., Bornat, Y., Romain, O., \& Kolbl, F. (2022). BIMMS: A versatile and portable system for biological tissue and electrode-tissue interface electrical characterization. HardwareX, e00387.} % Description
\end{cvskills}  
\begin{cvskills}
  \cvskill
    {[J02]} % Interest
    {Kolbl, F., Bornat, Y., Castelli, J., Regnacq, L., N’kaoua, G., Renaud, S., \& Lewis, N. (2021). Ic-based neuro-stimulation environment for arbitrary waveform generation. Electronics, 10(15), 1867.} % Description
\end{cvskills}  
\begin{cvskills}
  \cvskill
    {[J03]}
    {Tibar, H., Naudet, F., Kölbl, F., Ribot, B., Faggiani, E., N’kaoua, G., ... \& Benazzouz, A. (2020). In vivo validation of a new portable stimulator for chronic deep brain stimulation in freely moving rats. Journal of Neuroscience Methods, 333, 108577.}
\end{cvskills}  
\begin{cvskills}  
  \cvskill
    {[J04]}
    {De Roux, E., Terosiet, M., Kölbl, F., Boissière, M., Histace, A., \& Romain, O. (2019). OFDM-based electrical impedance spectroscopy technique for pacemaker-induced fibrosis detection implemented in an ARM microprocessor. Microprocessors and microsystems, 70, 38-46.}
\end{cvskills}  
\begin{cvskills}  
  \cvskill
    {[J05]}
    {De Roux, E., Degache, A., Terosiet, M., Kölbl, F., Boissière, M., Pauthe, E., ... \& Romain, O. (2019). Orthogonal Multitone Electrical Impedance Spectroscopy (OMEIS) for the Study of Fibrosis Induced by Active Cardiac Implants. Journal of Sensors, 2019.}
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[J06]}
    {Kölbl, F., N'Kaoua, G., Naudet, F., Berthier, F., Faggiani, E., Renaud, S., ... \& Lewis, N. (2014). An embedded deep brain stimulator for biphasic chronic experiments in freely moving rodents. IEEE transactions on biomedical circuits and systems, 10(1), 72-84.}
\end{cvskills}

\cvsubsection{International Conferences with comity}
\begin{cvskills}
  \cvskill
    {[C01]} % Interest
    {Couppey, T., Kolbl, F., Quoy, M., Romain, O., Regnacq, L., \& Giraud, R. (2022, July). Conduction block stimulation optimization by envelope modulation toward the reduction of onset response. In FENS.} % Description
\end{cvskills}  
\begin{cvskills}
  \cvskill
    {[C02]} % Interest
    {Bailleul, A., Claudel, J., De Gannes, F. P., N'Kaoua, G., Kolbl, F., Soulier, F., ... \& Renaud, S. (2021, November). In vitro impedance spectroscopy: A MEA-based measurement bench for myoblasts cultures monitoring. In 2021 XXXVI Conference on Design of Circuits and Integrated Systems (DCIS) (pp. 1-6). IEEE.} % Description   
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[C03]} % Interest
    {Regnacq, L., Giraud, R., Sanabria, A., Thota, A., Roversi, L., Rouhani, M., ... \& Kolbl, F. (2021, October). Evaluation of Stimulation Waveforms for Safe and Efficient Peripheral Nervous System Activation. In 2021 Biomedical Circuits and Systems Conference (BioCAS 2021):" Restoring Vital Functions by Electronics–Achievements, Limitations, Opportunities, and Challenges".} % Description 
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[C04]} % Interest
    {Kölbl, F., Boulboul, N., Commereuc, M., \& Bourdel, E. (2018, December). A microstrip resonator based sensor for GHz characterization of in vitro cell culture. In 2018 12th International conference on sensing technology (ICST) (pp. 319-323). IEEE.} % Description    
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[C05]} % Interest
    {Sotière, J., Terosiet, M., De Roux, E., Von Chong, A., Kölbl, F., Histace, A., \& Romain, O. (2018, November). Versatile SAR-ADC for Biomedical Applications. In 2018 New Generation of CAS (NGCAS) (pp. 9-12). IEEE.} % Description   
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[C06]} % Interest
    {Regnacq, L., Degache, A., Castelli, J., N'Kaoua, G., Bornat, Y., de Gannes, F. P., ... \& Bernus, O. (2018, September). Preliminary Investigation Towards Embedded Impedance Spectroscopy in Implanted Stimulators. In International Workshop on Impedance Spectroscopy (IWIS).} % Description   
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[C07]} % Interest
    {Degache, A., N'Kaoua, G., Lewis, N., Kolbl, F., \& Bernus, O. (2018, September). Preliminary Study of Fibrotic Cardiac Tissues Characterization Using Impedance Spectroscopy. In International Workshop on Impedance Spectroscopy (IWIS).} % Description   
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[C08]} % Interest
    {De Roux, E., Terosiet, M., Kölbl, F., Boissière, M., Pauthe, E., Histace, A., \& Romain, O. (2018, September). Toward an embedded OFDM-based system for living cells study by electrochemical impedance spectroscopy. In 2018 IEEE 20th International Conference on e-Health Networking, Applications and Services (Healthcom) (pp. 1-6). IEEE.} % Description     
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[C09]} % Interest
    {De Roux, E., Terosiet, M., Kölbl, F., Boissière, M., Histace, A., \& Romain, O. (2018, August). Toward an OFDM-Based Technique for Electrochemical Impedance Spectroscopy. In 2018 21st Euromicro Conference on Digital System Design (DSD) (pp. 484-487). IEEE.} % Description     
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[C10]} % Interest
    {De Roux, E., Terosiet, M., Kölbl, F., Chrun, J., Aubert, P. H., Banet, P., ... \& Romain, O. (2017, August). Wireless and portable system for the study of in-vitro cell culture impedance spectrum by electrical impedance spectroscopy. In 2017 Euromicro Conference on Digital System Design (DSD) (pp. 456-461). IEEE.} % Description     
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[C11]} % Interest
    {Capllonch-Juan, M., Kölbl, F., \& Sepulveda, F. (2017, July). Unidirectional ephaptic stimulation between two myelinated axons. In 2017 39th Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC) (pp. 230-233). IEEE.} % Description     
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[C12]} % Interest
    {Castelli, J., Kölbl, F., Siu, R., N'Kaoua, G., Bornat, Y., Mangalore, A., ... \& Lewis, N. (2017, July). An IC-based controllable stimulator for respiratory muscle stimulation investigations. In 2017 39th Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC) (pp. 1970-1973). IEEE.} % Description
\end{cvskills}  
\begin{cvskills}
  \cvskill
    {[C13]} % Interest
    {Kolbl, F., Juan, M. C., \& Sepulveda, F. (2016, October). Impact of the angle of implantation of transverse intrafascicular multichannel electrodes on axon activation. In 2016 IEEE Biomedical Circuits and Systems Conference (BioCAS) (pp. 484-487). IEEE.} % Description          
\end{cvskills}  
\begin{cvskills} 
  \cvskill
    {[C14]} % Interest
    {Juan, M. C., Kölbl, F., \& Sepulveda, F. (2016, September). Optimisation of the spatial discretisation of myelinated axon models. In 2016 8th Computer Science and Electronic Engineering (CEEC) (pp. 216-221). IEEE.} % Description  
\end{cvskills}  
\begin{cvskills}
  \cvskill
    {[C15]} % Interest
    {Kölbl, F., \& Demosthenous, A. (2015, August). A figure of merit for neural electrical stimulation circuits. In 2015 37th Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC) (pp. 2075-2078). IEEE.} % Description  
\end{cvskills}  
\begin{cvskills}
  \cvskill
    {[C16]} % Interest
    {Kölbl, F., Guillaume, R., Hasler, J., Joucla, S., Yvert, B., Renaud, S., \& Lewis, N. (2014, October). A closed-loop charge balancing fpaa circuit with sub-nano-amp dc error for electrical stimulation. In 2014 IEEE Biomedical Circuits and Systems Conference (BioCAS) Proceedings (pp. 616-619). IEEE.} % Description  
\end{cvskills}  
\begin{cvskills}
  \cvskill
    {[C17]} % Interest
    {Kölbl, F., Sabatier, J., N'Kaoua, G., Naudet, F., Faggiani, E., Benazzouz, A., ... \& Lewis, N. (2013, October). Characterization of a non linear fractional model of electrode-tissue impedance for neuronal stimulation. In 2013 IEEE Biomedical Circuits and Systems Conference (BioCAS) (pp. 338-341). IEEE.} % Description      
\end{cvskills}  
\begin{cvskills}    
  \cvskill
    {[C18]} % Interest
    {Kölbl, F., Zbrzeski, A., Syed, E., \& Renaud, S. (2010, November). In vivo electrical characterization of deep brain electrode and impact on bio-amplifier design. In 2010 Biomedical Circuits and Systems Conference (BioCAS) (pp. 210-213). IEEE.} % Description    
\end{cvskills}  
\begin{cvskills}   
  \cvskill
    {[C19]} % Interest
    {Zbrzeski, A., Hasler, P., Kölbl, F., Syed, E., Lewis, N., \& Renaud, S. (2010, November). A programmable bioamplifier on FPAA for in vivo neural recording. In 2010 Biomedical Circuits and Systems Conference (BioCAS) (pp. 114-117). IEEE.} % Description                   
\end{cvskills}

\cvsubsection{National Conferences}
\begin{cvskills}   
  \cvskill
    {[N01]} % Interest
    {Regnacq, L., Giraud, R., N'Kaoua, G., Renaud, S., Jung, R., Abbas, J., ... \& Romain, O. A model/hardware framework for arbitrary waveform stimulation of peripheral nerve fibers. In Neuro France 2021. } % Description                   
\end{cvskills}
\begin{cvskills}   
  \cvskill
    {[N02]} % Interest
    {Boulboul, N., Commereuc, M., Kölbl, F., \& Bourdel, E. Conception d’un capteur in-vitro de permittivité des tissus biologiques. Gdr Soc2. 2018} % Description                   
\end{cvskills}
\begin{cvskills}   
  \cvskill
    {[N03]} % Interest
    {Kölbl, F.; Guillaume, R.; Hasler, J.; Joucla, S.; Yvert, B.; Renaud, S.; Lewis, N. Circuit de stimulation nerveuse à contre-réaction d’équilibrage des charges sur FPAA. Gdr Soc-Sip 2014} % Description                   
\end{cvskills}

\cvsubsection{Talks}
\begin{cvskills}   
  \cvskill
     {Mai 2022} % Interest
    {\underline{Colloque CY :} The interplay of complex and coherent dynamics in brain function. \underline{Présentation :} Stimulation of nervous system with complex waveform stimuli} % Description                   
\end{cvskills}
\begin{cvskills}   
  \cvskill
    {FETCH 2018} % Interest
    {Diagnostic, Impedance-Sensing for imaging} % Description                   
\end{cvskills}
\begin{cvskills}   
  \cvskill
    {Scientific days of IJL Lab 2017} % Interest
    { toward reconfigurable circuits and systems interacting with biology} % Description                   
\end{cvskills}
\begin{cvskills}   
  \cvskill
    {FETCH 2017} % Interest
    { Activ Neuroprostetics: toward adaptive circuits} % Description                   
\end{cvskills}